Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Removed note about some scene graph components in application
Say application views RapidGL scenes
Second sentence of application paragraph has 'users' as subject

From there an application was created to view the resulting scenes.  It can
rotate the camera around the scene, as well as select objects in the scene and
drag them around.  It shows the current frame rate so we can evaluate the
performance of the scenes.  Some scene graph components that are not general
enough to be in the library were created at the application level.

>>>>

From there an application was created to view RapidGL scenes.  Users can
rotate the camera around a scene, as well as select objects and drag them.  It
shows the current frame rate so we can evaluate the performance of the scenes.
